Internship Summary: Mid-Term Review

### 2020-07-20 RapportStage/Rapport.tex
update monday
corrections biblio

\subsection{Alternative partitioning}

@@

We will take the simple case of the M{\o}ller-Plesset partitioning with a restricted Hartree-Fock minimal basis set as our starting point for this analysis. \\

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{RHFMiniBasRCV.pdf}
    \caption{\centering }
    \label{fig:RHFMiniBasRCV}
\end{figure}

Then we will compare the different partitioning using the same basis set. The \autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence in function of $R$ for the M{\o}ller-Plesset, the Epstein-Nesbet, the weak correlation and the strong coupling partitioning. We can see that

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{PartitioningRCV.pdf}
    \caption{\centering }
    \label{fig:RadiusPartitioning}
\end{figure}

@@

@@

\section{To do list}

\begin{itemize}
\item Corriger les erreurs dans la biblio
\item citation spin density wave et charge density wave
\end{itemize}

>>>>

\subsection{Alternative partitioning}\label{sec:AlterPart}

@@

We will take the simple case of the M{\o}ller-Plesset partitioning with a restricted Hartree-Fock minimal basis set as our starting point for this analysis. The electron 1 have a spin $\alpha$ and the electron 2 a spin $\beta$. Hence we can forget the spin part of the spin-orbitals and from now we will work with spatial orbitals. In the restricted formalism the spatial orbitals are the same so the two-electron basis set is: $\psi_1=Y_0(\theta_1)Y_0(\theta_2)$; $\psi_2=Y_0(\theta_1)Y_1(\theta_2)$; $\psi_3=Y_1(\theta_1)Y_0(\theta_2)$; $\psi_4=Y_1(\theta_1)Y_1(\theta_2)$.

The Hamiltonian $\bH(\lambda)$ is block diagonal because of the symmetry of the basis set. $\psi_1$ have the same symmetry as $\psi_4$ and there is an avoided crossing between these two states as we can see in \autoref{fig:RHFMiniBasRCV}.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{EMP_RHF_R10.pdf}
    \includegraphics[width=0.45\textwidth]{RHFMiniBasRCV.pdf}
    \caption{\centering }
    \label{fig:RHFMiniBasRCV}
\end{figure}

Then we can compare the different partitioning of \autoref{sec:AlterPart} using the same basis set. The \autoref{fig:RadiusPartitioning} shows the evolution of the radius of convergence in function of $R$ for the M{\o}ller-Plesset, the Epstein-Nesbet, the Weak Correlation and the Strong Coupling partitioning. We can see that

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\textwidth]{PartitioningRCV.pdf}
    \caption{\centering }
    \label{fig:RadiusPartitioning}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\textwidth]{CSF_RCV.pdf}
    \caption{\centering }
    \label{fig:RadiusCSF}
\end{figure}

@@
